ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-24 pyked.tex
more minor fixes

\pk{} is licensed under the permissive, open-source BSD 3-clause license. The
source code is publicly available on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}~\autocite{PyKED}. Installation instructions
are available in the online documentation at
\url{https://pr-omethe-us.github.io/PyKED/install.html} and can be done via binary
packages or from the source code.

>>>>

\pk{} is licensed under the permissive, open-source BSD 3-clause license. The
source code is publicly available on GitHub at \url{https://github.com/pr-omethe-us/PyKED},
and versioned releases are automatically archived via Zenodo~\autocite{PyKED}.
\pk{} can be installed via binary packages or the source code; the online documentation
provides detailed installation instructions at
\url{https://pr-omethe-us.github.io/PyKED/install.html}.
